Classless Java: Tuning Java Interfaces

### 2015-12-07 paper/sections/Formalization.tex
latest

\noindent The definition of $\mBody$ reconstruct the full set of supertypes $\Cs$ and then delegates the work to two others auxiliary functions:
 $\tops(m,\C_0)$%, $\shadow(\methods)$
 and $\override(\method,\method')$.

>>>>

\noindent The definition of $\mBody$ reconstruct the full set of supertypes $\Cs$ and then delegates the work to two other auxiliary functions:
 $\tops(m,\C_0)$%, $\shadow(\methods)$
 and $\override(\method,\method')$.
